### 2018-08-06 paper/design.tex

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
%The \ac{SPOR} protocol assumes a source of random nodes, %\eg through \ac{RPS}~\cite[\eg][]{} or \iac{DHT} based scheme~\cite[\eg][]{}.
The SPOR protocol assumes that each node knows a random subset of the system's participants at all time (\eg through Random-Peer-Sampling \cite{Jelasity_Voulgaris_Guerraoui_Kermarrec_van_Steen_2007}).
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

>>>>

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
\commentAL{A lot of description here, should only come in Section~\ref{sec:squad_overlay}}
This focuses on the node selection, \ie adds node selection on top of Sphinxes.
The \ac{SPOR} protocol assumes a source of random nodes, \eg through 
\ac{RPS}~\cite[\eg][]{BrahmsRPS} or \iac{DHT} based 
scheme~\cite[\eg][]{Octopus}.
Each node must be associated with a public key and some availability 
prediction.
\Ac{SPOR} selects nodes for a route uniformly randomly and uses the 
availability to maximize the availability of the entire route, \ie across 
layers.
As \ac{SPOR} assumes this source of random nodes, the network view (routing 
information) of each node depends on this source of random nodes, as does the 
fact of how decentralized the scheme becomes and whether the network toppology 
is fully, mostly or partly connected (network structure).
As \ac{SPOR} is designed, it selects nodes uniformly among all the nodes 
(communication model, node selection) that the source of random nodes provides.
Thus, ultimately, these also depends on the source of random nodes.

### 2018-08-06 paper/sphinxes.tex

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
excellent description in the original Sphinx paper~\cite{Sphinx}.

>>>>

\Textcite{Sphinx} designed \iac{UC} secure message format for mixes, called 
Sphinx.
Since it is \ac{UC} secure, it provably implements an ideal onion routing 
functionality.
\Ie, it provides bitwise unlinkability on the forward route \commentAL{Routes must be defined before that point}, hides the path 
length, makes replies indistinguishable from forward messages and resists 
tagging attacks.
It is also compact with only 224 bytes of header for a five-hop path with 
128-bit security.
Sphinx only provides one node per onion layer, in this section we extend Sphinx 
to Sphinxes, which allows for multiple nodes per onion layer.
(See \cref{fig:OR-POR}.)
As such, Sphinxes could be described as a bounded random-walk protocol, \ie the 
each node selects the next node from a set restricted by the source.

@@

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
excellent description in the original Sphinx paper~\cite{Sphinx}.

### 2018-08-06 paper/squad-overlay-design.tex
finished describing file transfer

\newcommand\fileid{\ensuremath{ID_{\text{f}}}}
\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}}
\newcommand\recdevice{\ensuremath{d^{(r)}_f}}

@@

In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
In addition, in \name, each file is associated with a random ID \fileid, that is part of \finfo.

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she compute \finfo, 
plus one reply header per chunk, and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.

@@

\newcommand\bitfield{\ensuremath{bf_f}}
\paragraph*{Chunks and bitfields}
Alice's file $f$ is located on one of her devices, \sendingdevice. 
Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded.

Bob receives $f$ on a device \recdevice. 
When one of his devices receives a chunk $c_i$ for $f$, it fetches the proper recipient \recdevice by looking into the \squad overlay sequence
for the line \texttt{RECEIVING<\sendingdevice, \fileid>} and forwards the file chunk to \recdevice.
Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.

Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
When one of Alice's devices receive Bob's bitfield \bitfield, 
it forwards \bitfield to \sendingdevice by looking for the line \texttt{RECEIVING<\sendingdevice, \fileid>} in the \squad overlay's sequence.
Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
and sends a chunk to Bob among the ones that were not already acknowledged by Bob.

\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
Messages in \name might arrive in a wrong order or fail. 
It is not unlikely that the file exchange stops before its transfer is done.
As a solution, \sendingdevice will restart periodically sending all chunks that were not acknowledged by Bob if the transfer hangs.
This solution ensures liveness by increasing network traffic (some chunks might be received several times), as will be seen in the evaluation.
It nevertheless allows reliable file transfer among a network of poorly connected nodes in a private manner.

>>>>

\newcommand\fileid{\ensuremath{ID_{\text{f}}}\xspace}
\newcommand\sendingdevice{\ensuremath{d^{(s)}_f}\xspace}
\newcommand\recdevice{\ensuremath{d^{(r)}_f}\xspace}

@@

In \name, we want file exchanges to remain private: these metadata are exchanged out-of-band.
In addition, each file is associated with a random \fileid, that is part of \finfo.

\paragraph*{Out-of-band initialization} 
When Alice wishes to send a file $f$ to Bob, she computes \finfo, 
plus one reply header per chunk, and sends the whole to Bob.
Still out-of-band, Bob replies with one forward header per chunk.

@@

\newcommand\bitfield{\ensuremath{bf_f}\xspace}
\paragraph*{Chunks and bitfields}
Alice's file $f$ is located on one of her devices, \sendingdevice. 
Each chunk $c_i \in f$ is uploaded to Bob through a unique route $\mathcal{H}_{c_i}$.
When $d_f$ is online, it periodically sends chunks of $f$ to Bob until $f$ is entirely uploaded.

Bob receives $f$ on a device \recdevice, but a chunk $c_i$ for $f$ might arrive on any of his devices. 
This device then fetches the address of the proper recipient \recdevice by looking for the line \texttt{RECEIVING<\recdevice, \fileid>} in its squad sequence, 
and forwards the file chunk to \recdevice.
Upon reception of the chunk, \recdevice verifies its integrity by computing its SHA1 hash $h_{c_i}$ and comparing it to $\finfo.h_{c_i}$.
If the chunk is valid, \recdevice updates its \emph{bitfield} \bitfield: this bit-array of size \nchunks is initialized with 0;
every time Bob successfully receives a chunk $c_i$, \recdevice sets the bit $\bitfield[i]$.
To acknowledge the chunk's reception, \recdevice sends \bitfield back to Alice, through a unique route $\mathcal{H}'_{c_i}$.

Reciprocally, acknowledgments can arrive to Alice on any on her devices, while only \sendingdevice can process it.
When one of Alice's devices receives Bob's bitfield \bitfield, 
it forwards \bitfield to \sendingdevice by getting its address on the line \texttt{RECEIVING<\sendingdevice, \fileid>} of the \squad overlay's sequence.
Upon reception of a bitfield \bitfield, \recdevice updates its knowledge of Bob's unreceived chunks of $f$,
and sends a chunk to Bob among the ones that were not already acknowledged by Bob, unless the file has been entirely received.

\commentAL{This is a shitty scheduler. Should I mention it? Rephrase? You have a citation to propose instead?}
Messages in \name might arrive in a wrong order or fail:
it is not unlikely that the file exchange stops before its transfer is done.
As a solution, if the transfer hangs, \sendingdevice will restart periodically sending chunks that were not acknowledged by Bob.
This solution ensures liveness over network efficiency (some chunks might be received several times), as will be seen in the evaluation.
It nevertheless allows reliable file transfer among a network of poorly connected nodes in a private manner.

### 2018-08-06 paper/system-model.tex

\name provides a private and fully decentralized file sharing service by exploiting 
%% is a distributed system made of
users' devices. 
We assume any two devices can communicate with one another as soon as one knows the address of the other (\eg using the Internet, \changeFT{possibly extended with NAT traversal techniques}). The devices owned by the same user (this user's \squad) know of each other.
%Thus, the devices from an \squad only know the mapping from devices to users for the devices in 
% the \squad they belong to.
We also assume that users can exchange some limited amounts of data 
out-of-band, \ie through some other channel than the network just mentioned (\eg 
using \ac{NFC} or QR codes).

%system model: explain e-squad, contrast with cloud

@@

In the following, we first describe \changeFT{how file sharing typically occurs when users rely on a cloud storage provider. We use this simple use case}
%a simple model of data sharing via cloud storage
to
highlight some of the desirable privacy properties of a file sharing service, before mapping them into our \changeFT{fully decentralized (a.k.a. P2P)}
context. 
We finally consider the additional privacy properties required to protect users from  network traffic analysis, which we propose to address through onion
routing, and detail our adversary model. \commentFT{I wasn't sure how to position onion routing: to me it is more a solution than a problem specification, and since we are describing what we want here (spec./problem space) I wasn't sure how much to highlight onion routing (solution space).} \commentFT{Terminology: Do we use both `fully decentralized' and `P2P', or do we favor one over the other?}

% We then add privacy properties and adversary models for onion
% routing to cover network traffic analysis.

\subsection{File sharing through a cloud storage provider}
\commentFT{Moving to subsections, to better highlight structure}

When sharing a file with Bob through a cloud provider, Alice only needs to upload this file from one of her devices to the cloud, and \changeFT{share a link to this file with Bob}. Bob in turn can download this file through the transmitted link onto one of his devices.

The use of the cloud provider, as a third party,
provides two main privacy properties, which we \changeFT{should preserve} when
moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
\begin{itemize}
\item Except for the cloud provider, Alice and Bob are the only \changeFT{users} who learn 
about Alice sharing a file with Bob; \sonja{narrow down to users?} \commentFT{Changed to users: we could also use entities/participants}
\item
  The composition and behavior of Alice and Bob's \squad remain hidden to each other, and to other users. I.e. Alice does not learn which devices Bob owns or uses, let alone how Bob uses them, and reciprocally. 
%%   Alice and Bob learn nothing about each others' devices, \ie 
%% they cannot map any device as belonging to each other or draw
%% inferences from their behavior.
The cloud provider, however, \changeFT{knows this information}. \sonja{expand to other users?} \commentFT{Done}
\end{itemize}

\subsection{Moving to a P2P environment}
A private P2P file sharing solution should retain
%% We want to keep
the privacy that
Alice and Bob already enjoy when a cloud provider functions
as a gatekeeper towards each other and other users.
\changeFT{Eschewing a cloud provider, as we propose to do, removes the privacy risks associated with a central brokering entity,}
% We go a step further by removing the cloud provider that may draw inferences from metadata even when the data itself is encrypted.
%Unfortunately, removing the cloud provider
\changeFT{but} also removes the gatekeeping a cloud provider provides, \changeFT{and exposes} users to friendly surveillance~\cite{FriendlySurveillance}
by other peers (other \name users including Alice and Bob). \sonja{removed: in
  an honest-but-curious setting}
\commentFT{Removed, as did not fit with the flow, but probably needed somewhere: `We give the definitions for the
security and privacy properties of \name in Section~\ref{security-discussion}.'} \changeFT{In particular other users might collude to observe some of the traffic, and gain knowledge regarding Alice's and Bob's interactions, the devices they own, and how they use them.}

%\subsection{Protecting against network traffic analysis in \name}
\subsection{The privacy properties and adversary model of \name}

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing \cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor its
owner. \changeAL{Thus, no information on the user's behavior (e.g. being online) can be infered through \name.} 
%and can thus not infer anything about a user's behavior such as being online.

>>>>

\name provides a private and fully decentralized file transfer service by exploiting 
%% is a distributed system made of
users' devices.  We assume any two devices can communicate with one
another as soon as one knows the address of the other (\eg using the
Internet, possibly extended with NAT traversal techniques). The
devices owned by the same user (this user's \squad) know of each
other. Other users' devices can help transfer the file from one user
to another but are not needed for storage.  We also assume that users
can exchange some limited amounts of data out-of-band, \ie through
some other channel than the network just mentioned (\eg using \ac{NFC}
or QR codes).
%system model: explain e-squad, contrast with cloud

@@

In the following, we first describe how file transfer typically occurs
when users rely on a cloud storage provider. We use this simple use
case to highlight some of the desirable privacy properties of a file
transfer service, before mapping them into our fully decentralized
(a.k.a. P2P\footnote{We use the terms \emph{fully decentralized} and
  \emph{P2P} interchangeably, and preferentially the latter for brevity.})
context.  We finally consider the additional privacy properties
required to protect users from inferences such as by network traffic
analysis and state our adversary model.

\subsection{File transfer via a cloud storage provider}

When sharing a file with Bob through a cloud provider, Alice only
needs to upload this file from one of her devices to the cloud, and
share a link to this file with Bob. Bob in turn can download this file
through the transmitted link onto one of his devices.

The use of the cloud provider, as a third party,
provides two main privacy properties, which we should preserve when
moving to a \ac{P2P}~\cite{DevilInMetadata} setting:
\begin{itemize}
\item Alice and Bob are the only users who learn 
about Alice sharing a file with Bob.
\item The composition and behavior of Alice and Bob's \squad remain
  hidden to each other, and to other users. I.e. Alice does not learn
  which devices Bob owns or uses, let alone how Bob uses them, and
  reciprocally.
\end{itemize} 
The cloud provider, however, has this information and any other
stemming from the users' interaction with the service, and can draw
inferences from metadata even when the data itself is encrypted, and
thus poses a threat to the users' privacy.

\subsection{Moving to a P2P environment}
A private P2P file transfer solution should retain the privacy that
Alice and Bob already enjoy when a cloud provider functions as a
gatekeeper towards each other and other users.  Eschewing a cloud
provider, as we propose to do, removes the privacy risks associated
with a central brokering entity, but also removes the gatekeeping a
cloud provider provides, and exposes users to friendly
surveillance~\cite{FriendlySurveillance}, in an honest-but-curious
setting, by other peers (other \name users including Alice and
Bob). In particular other users might collude to observe some of the
traffic, and gain knowledge regarding Alice's and Bob's interactions,
the devices they own, and how they use them.

\subsection{The privacy properties and adversary model of \name}

Friendly surveillance can be mitigated by ensuring security properties 
typically associated with onion routing, as defined by Camenisch and Lysianskay~\cite{CLOnionRouting}: 
% We combine the requirements from
% the \ac{P2P} setting with those from onion routing for anonymity.
% Camenisch and Lysianskaya \cite{CLOnionRouting} define security properties 
% for onion routing:
correctness, integrity, security (wrap resistance,
indistinguishability). These properties cover the concerns about
revealing to others that Alice shares a file with Bob in the first
place. In \name, we additionally derive the property of
device-unlinkability from the \ac{P2P} requirements, meaning that
using \name does not reveal the \squad a device belongs to nor its
owner. Thus, no information on the user's behavior (e.g. being online)
can be infered through \name.  \commentFT{Removed, as did not fit with
  the flow, but probably needed somewhere: `We give the definitions
  for the security and privacy properties of \name in
  Section~\ref{security-discussion}.'} \sonja{better here. Need to define
  device unlinkability, the rest is covered by Camenisch.}
